Transparency of COVID-19-related research - Analysis

### 2022-04-21 rmarkdown-covid-19-transparent-analysis.Rmd
edits to results and abstract
delete setwd()

# Loading the datasets
First, set working directory to the folder that has all the datasets in it using setwd() function and then run the following code:
```{r}
opendata <- read.csv(here("data", "covid_transparency_opendata.csv"))
```

>>>>

# Loading the datasets

```{r}
opendata <- read.csv(here("data", "covid_transparency_opendata.csv"))
```
